Title?

### 2019-08-21 April/paper_wc_recovered.tex
On hold.

Progressive second price auctions (PSPs) were proposed
in \cite{lazar}, \cite{diffserve} to provide a dynamic network service pricing
scheme to provide consistent services for network bandwith users.
\cite{diffserve} conducts a game theoretic analysis, deriving
optimal strategies for buyers and brokers, and further shows the existence
of networkwide market equilibria based on their game-theoretic
model. Constructing necessary and sufficient conditions for the stability
of the game allows the sustainability of any set
of service level agreement configurations between Internet service
providers to be determined.

We begin with a brief introduction to the distributed PSP auction for bandwith
sharing, first introduced by Lazar and Semret \cite{lazar}.
We define a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ network bandwidth users.
Suppose each user $i \in \mcI$ makes a bid $s_i^j = (p_i^j, d_i^j)$ to the
seller of resource $j$, where $p_i^j$ is the unit-price the user is willing to
pay and $d_i^j$ is the quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ is the profile of user $i$'s opponents. 
Using this classic PSP mechanism, \cite{lazar} shows that given the opponents
bids $s_{-i}$,
user $i$'s $\epsilon$-best response to seller $j$ is $s_i^j = (w_i^j, v_i^j)$
and is a Nash move
where $\epsilon > 0$ is the bid fee, $B_i =\sum_{j\in\mcI} b_i^j$ is user $i$'s
budget, and every user has an elastic demand function.
Based on the profile of bids $s^j = [s^j_1, \cdots , s^j_I]$, the seller applies
an allocation rule $a(s^j) = [a_1^j, \cdots , a_I^j]$, where $a^j_i$ is the quantity allocated
by $j$ to each user $i\in\mcI$ and $c^j_i$ is the cost charged to $i$ for
allocations awarded in auction $j$. 
An allocation is considered feasible if $a^j_i \le d_i^j$, and $c^j_i \le  p^j_i d_i^j$.

% MECHANISM
\subsubsection{The Mechanism}\label{mechanism}
The PSP auction as given in \cite{lazar} and \cite{semret} is designed for the
problem of network bandwidth allocation, and is analyzed as a noncooperative
game where $i\in\mcI$ agents buy the
fixed amount of bandwidth $d_i^j$ from sellers $j\in\mcI$.
The market price function (MPF) for a buyer-seller pair is,
% NEW MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    P_i^j(z, s_{-i})= \inf\bigg\lbrace y\ge 0 : 
    d_i^j - \sum_{p_k^j>y,k\ne i} d_k^j \ge z \bigg\rbrace,\\
\end{split}
\end{align}
and is the of minimum prices a user bids in
order to obtain bandwidth $z$ given opponent profile $s_{-i}$. 
The maximum available quantity of data in auction
$j$ at unit price $y$ given $s_{-i}^j$ is,
% NEW INVERSE DEMAND
\begin{align}\label{datapriceinverse}
\begin{split}
    D_i^j(y, s_{-i}) &= \bigg\lbrace D^j - \sum_{p_k^j>y,k\ne i} d_k^j  \bigg\rbrace,
\end{split}
\end{align}
where $D^j$ is the total amount of bandwith that user $j$ has to offer.
% DATA ALLOCATION RULE
For each $i \in \mcI$, the allocation from auction $j$ is,
% and so for profile $s_i$, for any $i \in \mcI$,
\begin{align}\label{dataallocation}
    a_i^j(s) &= \min\bigg\lbrace d_i^j, 
    \frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
\end{align}
Finally, we have the cost of the allocation,
% DATA COST
\begin{align}\label{datacost}
    c_i^j(s) = \displaystyle\sum_{k\ne i} 
p_k^j \big[a_k^j(0; s_{-i}^j)
    -a_k^j(s_i^j;s_{-i}^j)\big].
\end{align}

It was shown, in \cite{lazar}, that the mechanism may converge to a Nash market
equilibria for differentiated services
allocated between multiple agents when all players bid their real marginal valuation
of the bandwidth resource. In other words, the PSP constraints are
sufficient to attain the desirable property of truthfullness through incentive
compatibility. The pricing mechanism upholds the \emph{exclusion-compensation
principle}, user $i$
pays for its allocation so as to exactly cover the ``social opportunity cost"
which is given by the declared willingness to pay (bids) of the users who are
excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
revenue \cite{lazar}.
We have the definition of an elastic valuation function. In the PSP market, a
user is considered truthful if their bid price equals their marginal valuation,
i.e. $p_i^j = {\theta_i^j}'$.
\definition{\cite{lazar}}
A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
function} on $[0, D]$ if 
\begin{itemize}
    \item $\theta(0) = 0$,
    \item $\theta$ is differentiable,
    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
{\theta}'(\eta)
- \gamma(z - \eta)$. 
\end{itemize}

@@

\section{The Problem Model}
\subsection{The CMHK Market}

We begin to construct the model for a PSP data auction for  mobile users
particpating in CMHK's secondary data-sharing market.
Define $\mcI = \lbrace 1, \cdots, I\rbrace$ as the set of users who purchase or sell
data from other users. We again define the bidding profile for any user to be 
$s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ as the profile of user $i$'s opponents. 
As a cellular network is fully connected, we assume that a buyer submits bids directly to sellers via the
cellular network. We assume that users are selfish, and therefore
rational. 
 Users prefer to participate in the secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. 
Thus we assume that all users submit bids in order to maximize their
(private) valuation functions. 
In general, user preferences are defined by a utility function, $u$, which typically
represents a users' valuation of an allocation minus the price.
Absent the cost or revenue from trading data, CMHK users gain utility from consuming
data. 
We will assume that the user valuation satisfies the conditions for an
\emph{elastic demand function}, as in \cite{lazar}. 
As the CMHK market does not allow for brokers \cite{cmhk}, we determine that
the bid profiles must adhere to some additional restrictions, which we will
imply using the PSP bid profile notation.
A user's identity $i \in \mcI$ as a \textbf{subscript} indicates that the bid
belongs to a \textbf{buyer}, and a \textbf{superscript}, $j\in\mcI$, indicates
the bid belongs to a \textbf{seller}.
Suppose $i$ is buying from $j$. The bid is represented by $s_i^j = (d_i^j, p_i^j)$, 
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
auctions; if a user $i$ does not submit a bid to $j$, or vice versa, we simply set $s_i^j =
(0,0)$. Naturally, in a live auction, if a buyer does
not submit a bid to a seller, then this implies $s_i^j = 0$ for both buyer $i$
and seller $j$.
A seller $j$ places an ask $s_i^j = (d_i^j, p_i^j)$, meaning $j$ is offering a
quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$ 
with reserve unit price $p_i^j \in p^j = [p_i^j]_{i\in\mcI}$ to buyer $i$. We emphasize that we allow for $s_i^j$ to
stand for a buyer or sellers' bid, the \emph{direction} of the bid (vector) is determined
by the user type, whether or not they are  a buyer or a seller. 
To further clarify our analysis, we will emphasize the separation of buyers and
sellers using
$s_i$ and $s^j$, indicating if a bid is from a buyer or a seller.
In other words, a bid $s^j =
[s_i^j]_{j\in\mcI}$ is understood as an offer of data by seller $j$ in the CMHK
secondary market. The notational conventions of the bid vectors are essentially 
slices of the grid, $s^j = [s_i^j]_{i\in\mcI}$ denotes a sellers' profile, and $s_i =
[s_i^j]_{j\in\mcI}$ denotes a buyers' profile. 
Furthermore, noting that this is a simplification for ease of notation, we let $D^j = \sum_{i\in\mcI}
d_i^j$ be the total amount of data $j$ has to sell, and $D_i = \sum_{j\in\mcI}
d_i^j$ represent the
total amount of data requested by buyer $i$. 
Finally, we assume that data is a unary resource belonging to the seller, and
therefore can identify each local auction
with the identity of the seller $j\in\mcI$.

Consider the grid of bid proiles, $s$, representing the distributed PSP auction
mechanism in the CMHK market, each buyer $i$ will
have information from each seller $j$, as well as opponent profiles $s_{-i}$
from each auction in which it is participating, and therefore
in the extreme case, buyer $i$ gains access to the full grid $s$. The extreme with respect to
$i$ is the case where buyer $i$ will participates in all auctions $j\in\mcI$
(SHOULD I PROVE THIS OR TOO TRIVIAL?). However, 
sellers can only gain information about the market grid by observing buyer
behavior in their local auction.
In our current formulation, we do not allow a seller to host multiple
auctions(FUTURE WORK?). Thus, only the buyers are able to directly and globally
influence the CMHK market dynamics, with the sellers taking a secondary role
(FIND IN ANOTHER PAPER FOR SUPPORT OR OBVIOUS ENOUGH?).

@@

We are not concerned with network
bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, however
we reason that there remains an optimal user strategy. As a user no longer needs
to bid on a complete (but arbitrary)
cluster of nodes with minimum bandwidth allocation (defined as a route in
\cite{semret}), we reason that a buyer may opt-out of auctions, maximizing its
utility while minimizing the number of positive bids submitted to the overall
market. We define an \textbf{opt-out function}, $e$, as a function that when composed with our user type to describes
its market behavior. In a general sense, $e$ applies our user \emph{strategy}
to the PSP rules.
Our reserve price function is determined by the subset of nodes participating in the
auction, where the seller is its own auctioneer. This implies that the influence of the greater market on the individual
auctions will be influenced only by the submission of bids from buyers to
sellers. As a buyer may have access to multiple auctions, the sellers will be
dynamically influenced by the market via the $\epsilon$-best replies from the
buyers. We demonstrate that as the valuation function of seller $j$ is dependent
on the buyers demand, and further show evidence of symmetry in the strategies of
buyers and sellers.

@@

% OPT-OUT BUYER
We define each buyer as a user $i\in\mcI$ with quasi-linear utility
function $\theta_i$, the value of the allocation minus the cost,
\begin{equation}\label{buyerutility}
    u_i = \theta_i \circ e_i(a) - c_i,
\end{equation}
where $e_i : [0, \infty)^I \rightarrow [0,\infty), \ \forall \ i \in \mcI$. 
We extend the P2P rules described
in \cite{semret} to account for a set of \emph{local} data-exchange markets.

@@

Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
is also reasonable to expect that a seller may come close to using their
entire data cap, and only sell the fractional overage. In this case, we
determine that buyers must split their bids among multiple sellers. 
We propose the following strategy, 
% BUYER STRATEGY
{
\proposition{(Opt-out buyer strategy)}\label{buyerstrategy}
Define any auction duration to be $\tau \in [0,\infty)$. 
Let $i\in\mcI$ be a buyer and fix all other buyers' bids $s_{-i}$ at time
$t\in\tau$. % For any allocation $a$ at time $t$, let
% OPT-OUT BUYER STRATEGY
%\begin{equation}\label{opt-out}
    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} 
    %e_i^j(a) \triangleq a_i^j,
%\end{equation}
%and define,
Define the composition,
$$
     e_i^j \circ a = e_i^j(a) = \frac{a_i^j}{j},
$$
to be the buyer strategy with respect to quantity, and the set,
% MIN SET
$$
    \mcI_i(n) =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
n}\sum_{j\in\mcI'} D^j,
$$
where buyer $i$ chooses its seller pool by determining $n$, where
\begin{equation}\label{buyercoordinate}
    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} \frac{d^n}{d_i}
    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} d^n
    n = \min( j\ \vert\ j\in \mcI_i(n): j D^j\ge D_i),
\end{equation} 
The buyer strategy produces a minimal subset of sellers $\in \mcI$, so for any
fixed $n$ we will denote this subset,
\begin{equation}\label{sellers}
    \mcI_i \subset \mcI.
\end{equation}  
Now let $j^* = n \le I$, and define,
\begin{equation}\label{opt-minallocation}
    e_i(a) \triangleq e_i^{j^*}(a)
\end{equation}
$\forall \ j \in \mcI_i$.
As (\ref{opt-minallocation}) holds $\forall \ j\in\mcI_i$,
we have that $e$ defines an optimal feasible strategy for buyer $i$ from time $t$ to time $(t+1) \in\tau$.
}\\
\textbf{Proof:}

We assume that a buyer wants to fufill their data requirement.
In the case that there exists a seller who can completely satisfy a buyers'
demand, $j^*=1$, $\vert \mcI_i\vert =1$ and (\ref{buyercoordinate}) holds. If such a buyer does not exist,
as the set $\mcI_i$ is an ordered set, $i$ may discover 
$j^*$ by computing $\mcI_i$.
If we suppose that $D_i >
\sum_{j\in\mcI}D^j$, then $j^* > I$ and $\mcI_i = \emptyset$. 
We model the ISP as a seller $\kappa$ with bid $s^\kappa =(D^\kappa, P^\kappa)$,
where $D^\kappa > D^j, \
\forall \ j\in\mcI_i$, and
$P^k$ represents the overage fee for data set by the ISP, which is also the upper bound of the sellers'
pricing function, and so again (\ref{buyercoordinate}) holds.
Now consider some $k \ne i \in \mcI$ where $p_i^j = p_k^j$. 
The allocation rule (\ref{dataallocation}) determines that the data will be split proportinally
between all buyers with the same unit price. 
It is possible that the resulting partial allocation of data to $i$ and $k$
would not satisfy some demand. As the two cases $i$ and $k$ are the same, we consider such
a seller $i$. Suppose seller $j$ updates its
bid to reflect the new data quantity, so that $d_i^{j(t+1)} < d_i^{j(t)}$ (NOTE:
IS THE DIRECTION OF THE BID CONFUSING?, i.e. $d_i^j$ from buyer (rhs) or seller
(lhs) unclear? does it matter?) Then, by the definition of $\ell_i$, we can
only have that $j \ni \mcI_i$, or that $n$ has been increased, and new seller(s)
enter the pool. 
Additionally, we consider that at time $(t+1)$, we can have a 
new buyer $k$, where $p_k^j > p_i^j, \ \forall \ j \ \in \mcI_i$, in other
words, a new buyer $k$ may enter the market with a better price. In this case, by (\ref{buyercoordinate}), $i$ will increase the value of
$n$ so that
$$
    e_i^{j(t+1)}(a) = e_i^{j(t)}(a) - e_k^{j(t)}(a),
$$
and the subset $\mcI_i$ is large enough to balance the additional demand from
$k$. Thus, as in each case we have that $i$ is able to satisfy thier demand,
and we determine that the opt-out strategy is optimal.

@@

Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
which is distributed across the secondary market via bids in local auctions. 
Buyer behavior is influenced by opponent bid profiles from multiple auctions.
The valuation of any user, however, is a function of the entire marketplace.  
We first define the ``inverse" demand for any buyer $i$,
% BUYER REVENUE 
\begin{equation}\label{buyerinversedemand}
    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
        \rho^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
\end{equation}
For a given demand $\rho^j$, $f_i$ maps the $z$th unit of data to the lowest
possible unit price. \\
\textbf{Remark:} In a coordinated bid, $f_i$ is such that
$i$ could still bid in \emph{any} auction $j\in\mcI$.
Naturally, the coordinated bid is the
lowest unit cost of the buyer to participate in all auctions, and corresponds to
the maximum reserve price amongst the sellers.

>>>>

\subsubsection{Allocation using PSP}

We begin with a brief introduction to the generalized distributed PSP auction, first introduced by Lazar and Semret \cite{lazar}.
We define a set of $\mcI = \lbrace 1,\cdots,I\rbrace$ users.

Suppose each user $i \in \mcI$ makes a bid $s_i^j = (p_i^j, d_i^j)$ to the
seller of resource $j$, where $p_i^j$ is the unit-price the user is willing to
pay and $d_i^j$ is the quantity the user desires. The \emph{bidding profile} forms a grid, $s \equiv
[s_i^j] \in \mcI \times \mcI$, and $s_{-i} \equiv [s_1^j , \cdots , s_{i-1}^j , s_{i+1}^j , \cdots
, s_I^j]_{j\in\mcI}$ is the profile of user $i$'s opponents.

Using this classic PSP mechanism, \cite{lazar} shows that given the opponents
bids $s_{-i}$,
user $i$'s $\epsilon$-best response to seller $j$ is $s_i^j = (w_i^j, v_i^j)$
and is a Nash move
where $\epsilon > 0$ is the bid fee, $B_i =\sum_{j\in\mcI} b_i^j$ is user $i$'s
budget, and every user has an elastic demand function.

Based on the profile of bids $s^j = [s^j_1, \cdots , s^j_I]$, the seller applies
an allocation rule $a(s^j) \in d^j = [d_1^j, \cdots , d_I^j]$, where $a^j_i$ is the quantity allocated
by $j$ to each user $i\in\mcI$ and $c^j_i$ is the cost charged to $i$ for
allocations awarded in auction $j$. 
An allocation is considered feasible if $a^j_i \le d_i^j$, and $c^j_i \le  p^j_i d_i^j$.

Each user has a \emph{valuation} $\theta(a(s)$, which is the total value of its allocation.

We intend to show that our PSP constraints are
sufficient to attain the desirable property of truthfullness through incentive compatibility. We
reason, due to our pricing mechanism, that our formulation upholds the \emph{exclusion-compensation
principle}, and is a valid progressive second price auction to the extent that buyer $i$
pays for its allocation so as to exactly cover the ``social opportunity cost"
which is given by the declared willingness to pay (bids) of the users who are
excluded by $i$'s presence, and thus also compensates the seller for the maximum lost potential
revenue \cite{lazar}.

We are not concerned with network
bottlenecks, which is purely a bandwidth problem, as in \cite{semret}, however
we reason that there remains an optimal user strategy. As a user no longer needs
to bid on a complete (but arbitrary)
cluster of nodes with minimum bandwidth allocation (defined as a route in
\cite{semret}), we reason that a buyer may opt-out of auctions, maximizing its
utility while minimizing the number of positive bids submitted to the overall
market. We define an \textbf{opt-out
value}, $e$, as a function that when composed with our user type to describes
its market behavior. In a general sense, $e$ is %the expectation 
a function that maps a buyer $i$ to matching seller(s).

We have the transform $e: \mathcal{X} \rightarrow \mathcal{Y}$, where
$\mathcal{Y} \subset \mathcal{X}$, and any
composition of the opt-out value $e$ with another function $x \in \mathcal{X}$
results in the scalar application of $e$ to $x$. In other words, for any
$x\in\mathcal{X}$, and $\mathcal{Y} \subset \mathcal{X}$,
$$
    e\circ x = \begin{cases} e(x), \qquad &x \in \mathcal{Y} \\
                             0, \qquad &x \ni \mathcal{Y}.
\end{cases}
$$
% OPT-OUT BUYER
We define a \emph{opt-out buyer} as a user $i\in\mcI$ with quasi-linear utility
function, the value of the allocation minus the cost,
\begin{equation}\label{buyerutility}
    u_i = \theta_i \circ e - c_i,
\end{equation}
where $e(\theta_i) : [0, \infty)_{i\in\mcI} \rightarrow [0,\infty)_{i\in\mcI}$. 
We extend the P2P rules described
in \cite{semret} to account for a set of \emph{local} data-exchange markets.
Our reserve price function is determined by the subset of nodes participating in the
auction, where the seller is its own auctioneer. This implies that the influence of the greater market on the individual
auctions will be influenced only by the submission of bids from buyers to
sellers. As a buyer may have access to multiple auctions, the sellers will be
dynamically influenced by the market via the $\epsilon$-best replies from the
buyers. We demonstrate that as the valuation function of seller $j$ is dependent
on the buyers demand, that the strategies of buyers and sellers may differ
drastically depending on the market.

@@

\section{The Problem Model}
\subsection{The Secondary Market}

We define the set of users, $\mcI = \lbrace 1, \cdots, I\rbrace$, who purchase or sell
data from other users. A buyer submits bids directly to sellers, where we
assume that all users submit bids in order to maximize their
(private) valuation functions.

(TERRIBLE, FUTURE WORK) public information in the
secondary market consists of a set of offers that are published by users
wishing to sell their data overage.

A user's identity $i \in \mcI$ as a subscript indicates that the user
is a buyer, and a superscript indicates the seller.
Suppose user $i$ is buying from user $j$. A bid $s_i^j = (d_i^j, p_i^j)$,
meaning $i$ would like to buy from $j$ a quantity $d^j_i$ and is willing to pay
a unit price $p^j_i$. Without loss of generality, we assume that all users bid in all
auctions; if a user $i$ does not submit a bid to $j$, we simply set $s_i^j = (0,0)$.
A seller $j$ places an ask $s_i^j = (d_i^j, p_i^j)$, meaning $j$ is offering a
quantity $d_i^j \in d^j = [d_i^j]_{i\in\mcI}$ 
with reserve unit price $p^j = [p_i^j]_{i\in\mcI}$. $D^j = \sum_{i\in\mcI}
d_i^j$ is the total amount and $D_i = \sum_{j\in\mcI} d_i^j$ is the
total amount of data required by a buyer $i$. Naturally, we define $P_i$ and
$P^j$ in the same way.
We emphasize that we allow for $s_i^j$ to
stand for a buyer or sellers' bid, determined by whether or not the user is a
buyer or seller. In other words, a bid $s^j$, the bid is understood as an offer in the secondary
market; we assume that data is a unary resource belonging to the seller, and
therefore can identify the data (for sale) with the identity of the user.
To further clarify our analysis, we will emphasize the separation of buyers and
sellers by denoting vectors bid as slices of the
grid, i.e. $s^j = [s_i^j]_{i\in\mcI}$ will denote a sellers' profile, and  $s_i =
[s_i^j]_{j\in\mcI}$ denotes a buyers' profile. 
The notational conventions given by the slices $s_i$
and $s^j$ will be used indicate if a bid is from a buyer or a seller. However,
we note that this is a simplification for ease of notation, and considering the
grid $s$ in a distributed setting, each buyer $i$ will
have information from each auction in which it is participating, and therefore
in the limit will have access to the full grid $s$. However, 
sellers can only gain information about the market grid by observing buyer
behavior in their local auction.
In our current formulation, we do not allow a seller to host multiple auctions(FUTURE WORK).

% MECHANISM
\subsection{Data Auction Mechanism}\label{mechanism}
We now proceed to formally define the PSP auction, which determines the actions 
buyers and sellers in the secondary market, which we will denote the \emph{data}
PSP rules.
The market price function (MPF) for a buyer in the secondary market
can be described as follows:
% NEW MARKET PRICE
\begin{align}\label{dataprice}
\begin{split}
    &\bar{P}_i(z, s_{-i}) =\displaystyle\sum_{j\in\mcI}P_i^j(z_i^j,
s_{-i}^j) \circ e_i^j \\
    &= \sum_{j\in\mcI}\bigg(\inf\bigg\lbrace y\ge 0 : 
    {D_i^j}(y,s_{-i}^j) \ge e_i^j(z) \bigg\rbrace \bigg),\\
\end{split}
\end{align}
and is interpreted as the aggragate of minimum prices that buyer $i$ bids in
order to obtain
data amount $z$ given opponent profile $s_{-i}$. We note that
the total minimum price for the buyer must be an aggragation of the
\emph{individual} prices of the buyers as it is possible that the reserve prices of the individual sellers may vary.
%To simplify the notation, we define $z_i^j = d^j / \vs_i^j$ opt-out
%buyer $i$'s bid quantity. 
The maximum available quantity of data in auction
$j$ at unit price $y$ given $s_{-i}^j$ is: 
% NEW ALLOCATION RULE
\begin{align}
\begin{split}\label{datacomposed}
    D_i^j(y,s_{-i}^j) = \bigg\lbrack D^j - \sum_{p_k^j> y} d_k^j\bigg\rbrack^+,
\end{split}
\end{align}
it follows that the inverse price function is aggregated over all local auctions
$j\in \mcI$,
% NEW INVERSE DEMAND
\begin{align}\label{datapriceinverse}
\begin{split}
    \bar{D}_i(y, s_{-i}) &= \displaystyle\sum_{j\in\mcI}\bigg(\sup\bigg\lbrace z\in \big[ 0,
    D^j \big] : \\
    &\bar{P_i}(z,s_{-i}^j) < y\bigg\rbrace\bigg).
\end{split}
\end{align}
% DATA ALLOCATION RULE
The resulting data allocation rule is a function of the local market
interactions between buyers and sellers over all local auctions, as is composed with $i$'s opt-out value, so that for each $i \in \mcI$, the
allocation from auction $j$ is,
% and so for profile $s_i$, for any $i \in \mcI$,
\begin{align}\label{dataallocation}
    \bar{a}_i^j(s) &= a_i^j(s) \circ e \\
    &= \min\bigg\lbrace e_i^j\circ D_i,
    \frac{d_i^j}{\sum_{p_k^j= p_i^j}d_k^j} e_i\circ D_i^j(p_i^j,s_{-i}^j)\bigg\rbrace.
\end{align}
Finally, we must have that the cost to the buyer adheres to the second price
rule for each local auction, with total cost to buyer $i$,
% DATA COST
\begin{align}\label{datacost}
\begin{split}
    \bar{c}_i(s) &= \displaystyle\sum_{j\in\mcI} 
p^j \bigg(\bar{a}_i^j(0; s_{-i}^j)
    -\bar{a}_i^j(s_i^j;s_{-i}^j)\bigg).
\end{split}
\end{align}

@@

We assume that users are selfish, and therefore
rational. Users prefer to participate in the secondary market as it allows them to purchase
additional data for a cost less than the overage fee set by the ISP. 
In general, user preferences are defined by a utility function, which typically
represents a users' valuation of an allocation minus the price, 
\begin{align*}
    u &: S \rightarrow (-\infty, \infty) \\
          & s \rightarrow u(s).
\end{align*}
Absent the cost or revenue from trading data, CMHK users gain utility from consuming
data. 
We will assume that the user valuation satisfies the conditions for an
\emph{elastic demand function}: 
\definition{\cite{lazar}}
A real valued function, $\theta(\cdot): [0,\infty) \rightarrow [0,\infty)$, is an \emph{(elastic) valuation
function} on $[0, D]$ if 
\begin{itemize}
    \item $\theta(0) = 0$,
    \item $\theta$ is differentiable,
    \item ${\theta}' \ge 0$, and ${\theta_i}'$ is non-increasing and continuous,
     \item There exists $\gamma > 0$, such that for all $z \in [0,D]$,
${\theta}'(z) > 0$ implies that for all $\eta \in [0, z), {\theta}'(z) \le
{\theta}'(\eta)
- \gamma(z - \eta)$. 
\end{itemize}
The user valuation

@@

@@

Although it is possible for a seller to fully satisfy a buyer $i$'s demand, it
is also reasonable to expect that a seller may come close to using their
entire data cap, and only sell the fractional overage. In this case, we
determine that buyers must split their bids among multiple sellers. 
We propose the following strategy, 
% BUYER STRATEGY
{
\proposition{(Opt-out buyer strategy)}\label{buyerstrategy}
Define any auction duration to be $\tau \in [0,\infty)$. 
Let $i\in\mcI$ be a buyer and fix all other buyers' bids $s_{-i}$ at time
$t\in\tau$. % For any allocation $a$ at time $t$, let
% OPT-OUT BUYER STRATEGY
%\begin{equation}\label{opt-out}
    %e_i^j(a) \triangleq \frac{a_i^j}{\vs_i^j} 
    %e_i^j(a) \triangleq a_i^j,
%\end{equation}
%and define,
Define the composition,
$$
    e_i^j(a) = a_i^j \circ e,
$$
and the set,
% MIN SET
$$
    \mcI_i(n) =\argmax_{\mcI' \subset \mcI, \vert\mcI'\vert =
n}\sum_{j\in\mcI'} D^j,
$$
where buyer $i$ chooses its seller pool by determining $n$, where
\begin{equation}\label{buyercoordinate}
    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} \frac{d^n}{d_i}
    %n = \argmin_{\ell_i}(j \in \ell_i : \displaystyle\sum_{n} d^n
    n = \min( j\ \vert\ j\in \mcI_i(n): j D^j\ge D_i),
\end{equation} 
Now let $j^* = n \le I$, and define,
\begin{equation}\label{opt-minallocation}
    e_i^j(a) \triangleq e_i^{j^*}(a).
\end{equation}
The buyer strategy produces a minimal subset of sellers $\in \mcI$, so for any
fixed $n$ we will denote this subset,
\begin{equation}\label{sellers}
    \mcI_i \subset \mcI.
\end{equation}  
As (\ref{opt-minallocation}) holds $\forall \ j\in\mcI_i$,
we have that $e$ defines an optimal feasible strategy for buyer $i$ from time $t$ to time $(t+1) \in\tau$.
}\\
\textbf{Proof:}

We assume that a buyer wants to fufill their data requirement.
In the case that there exists a seller who can completely satisfy a buyers'
demand, $j^*=1$, $\vert \mcI_i\vert =1$ and (\ref{buyercoordinate}) holds. If such a buyer does not exist,
as the set $\ell_i$ is an ordered set, $i$ may discover 
$j^*$ by computing $\ell_i$. If we suppose that $D_i >
\sum_{j\in\mcI}D^j$, then $j^* > I$ and $\ell_i = \emptyset$. 
We model the ISP as a seller $\kappa$ with bid $s^\kappa =(D^\kappa, P^\kappa)$,
where $D^\kappa > D^j, \
\forall \ j\in\mcI_i$, and
$P^k$ represents the overage fee for data set by the ISP, which is also the upper bound of the sellers'
pricing function, and so again (\ref{buyercoordinate}) holds.
Now consider some $k \ne i \in \mcI$ where $p_i^j = p_k^j$. 
The allocation rule (\ref{dataallocation}) determines that the data will be split proportinally
between all buyers with the same unit price. 
It is possible that the resulting partial allocation of data to $i$ and $k$
would not satisfy some demand. As the two cases $i$ and $k$ are the same, we consider such
a seller $i$. Suppose seller $j$ updates its
bid to reflect the new data quantity, so that $d_i^{j(t+1)} < d_i^{j(t)}$ (NOTE:
IS THE DIRECTION OF THE BID CONFUSING?, i.e. $d_i^j$ from buyer (rhs) or seller
(lhs) unclear? does it matter?) Then, by the definition of $\ell_i$, we can
only have that $j \ni \mcI_i$, or that $n$ has been increased, and new seller(s)
enter the pool. 
Additionally, we consider that at time $(t+1)$, we can have a 
new buyer $k$, where $p_k^j > p_i^j, \ \forall \ j \ \in \mcI_i$, in other
words, a new buyer $k$ may enter the market with a better price. In this case, by (\ref{buyercoordinate}), $i$ will increase the value of
$n$ so that
$$
    e_i^{j(t+1)}(a) = e_i^{j(t)}(a) - e_k^{j(t)}(a),
$$
and the subset $\mcI_i$ is large enough to balance the additional demand from
$k$. Thus, as in each case we have that $i$ is able to satisfy thier demand,
and we determine that the opt-out strategy is optimal.

@@

Buyer $i$'s valuation is interpreted as a unit valuation $\theta_i$,
which is distributed across the secondary market via bids in local auctions. 
Buyer behavior is influenced by opponent bid profiles from multiple auctions.
The valuation of any user, however, is a function of the entire marketplace.  
We first define the ``inverse" demand for any buyer $i$,
% BUYER REVENUE 
\begin{equation}\label{buyerinversedemand}
    f_i(z) \triangleq \inf\big\lbrace y\ge 0:
        \rho_i^j(y) \ge z, \ \forall \ j \in \mcI\big\rbrace.
\end{equation}
For a given demand $\rho^j$, $f_i$ maps the $z$-th unit of data to the lowest price at
which $i$ could still bid in \emph{any} auction $j\in\mcI$.
Naturally, this is the
lowest unit cost of the buyer to participate in all auctions, and corresponds to
the maximum reserve price amongst the sellers.

The seller is represented by a similar function, however a seller only has a
single auction, and is indirectly influenced by the buyers in other auctions, and so from the perspective of the
seller we have a more direct interpretation of revenue.
We define the ``inverse" of the buyer demand function for seller $j$ as revenue at unit price $y$. 
% SELLER REVENUE 
\begin{equation}\label{sellerinversedemand}
    f^j(z) \triangleq \sup\big\lbrace y\ge 0:
        \rho_i^j(y) \ge z, \ \forall \ i \in \mcI\big\rbrace,
\end{equation}
where $f^j$ maps to the highest possible unit data price.
Thus we have the following Lemma. 
{
\lemma{(User valuation)}
For any buyer $i$, the valuation of seller $j$'s data may be modeled as,
\begin{equation}\label{singlevaluation}
    \theta_i \circ e_i^j = \int_0^{e_i^j(a)} f_i(z) \ dz,
\end{equation}
it follows that 
\begin{equation}\label{buyervaluation}
    \theta_i \circ e = \displaystyle\sum_{j\in\mcI}
 \int_0^{e_i^j(a)} f_i(z) \ dz.
\end{equation}
Similarly, seller $j$'s valuation is,
\begin{equation}\label{sellervaluation}
    \theta^j \circ e = \displaystyle\sum_{i\in\mcI}
 \int_0^{e_i^j(a)} f^j(z) \ dz.
\end{equation}
}
\textbf{Proof:} 
We assume that a buyer wants to minimize the cost of purchasing their data
requirement, at the same time ensuring they get the full allocation $e_i(a)$,
and so must minimally meet $j$'s reserve price.
A seller will try to maximize profit for any given allocation $a$,
and will try to sell all of its data, and so 
$d_i^j = e_i \rightarrow \sum_{i\in{\mcI}} d_i^j = D^j =
\sum_{i\in\mcI} e_i$,
The remainder of the proof follows as in \cite{semret}. (REALLY THOUGH?)
(THERE MUST BE A CLEARER WAY TO DESCRIBE THE RELATIONSHIP)

The sellers' natural utility is the potential
profit $u^j = \theta^j\circ e$, where $\theta^j$ is the
potential revenue from the sale of data composed with each buyers' opt-out value, $e_i(a)$. 
We have chosen to omit the original cost of the data
paid to the ISP, as a discussion of mobile data plans is outside the scope of this
paper.
